INTELLIGENT SYSTEMS

### 2021-04-15 papers/paper_8.tex
finish 8.2

>>>>

\subsection{RELATED WORK}
Methods such as generative trackers have been developed for finding positions 
in which to find the best candidate during the tracking process. Good 
results have been achieved by compound trackers \cite{0893551105} \cite{0893551118}. Networks such as 
RNNs \cite{0893551121} can be used to predict possible target positions in each frame. 
However, these types of networks have not yet achieved satisfactory results. 
Some methods instead train a CNN offline while the test is done online. Unfortunately, 
these models are not fast. Other models instead if they fail a first 
time, then they will always fail until the target returns to the search region. 
Methods such as \cite{0893551129} \cite{0893551134} search for the target template in subsequent frames 
in the same position, obtaining better performance than methods based on 
similarity but nevertheless are not robust to distracting elements. The proposed 
method instead takes into account both the background patches and 
the target template patches in order to make comparisons on similarities.
